
# 2-6
```{r}
score <- c(65, 75, 85, 95, 100, 70, 80, 90, 95, 100, 75, 85, 95, 100, 80, 90, 95, 100, 85, 95, 100, 90, 95, 100, 95, 100, 100)
hist(score, main="")

```

# 2-7
```{r}
rv <- c(0.8, 0.9, 1.0, 1.1, 1.2, 1.3, 1.4, 1.5, 1.6, 1.7, 1.8, 1.9, 2.0, 2.1, 2.2, 2.3, 2.4, 2.5, 2.6, 2.7, 2.8, 2.9, 3.0, 3.1, 3.2, 3.3, 3.4, 3.5, 3.6, 3.7, 3.8, 3.9, 4.0, 4.1, 4.2, 4.3, 4.4, 4.5, 4.6, 4.7, 4.8, 4.9, 5.0, 5.1, 5.2, 5.3, 5.4, 14, 17, 18, 19, 21, 21, 23, 25, 27, 28, 32, 34, 36, 41, 42, 44, 48, 49, 51, 54, 59, 60, 61, 62, 80, 240)
hist(rv, main="",xlab="CRP", breaks=20)

```

# 2-8
```{r}
# Install forcats if not already installed
# install.packages("forcats")

# Load libraries
library(ggplot2)
library(forcats)


# Data
transp <- c("bycicle", "bus", "bus", "walking", "bus", "bycicle", "bycicle",
            "bus", "bus", "bus" , "bycicle", "bus", "bycicle", "bycicle", 
            "walking", "bus", "bus", "bicycle", "bicycle", "walking", "walking",
            "bicycle", "bus", "bus", "bus", "bus", "bicycle", "bus", "bus",
            "bicycle", "bicycle", "bicycle")
dat1 <- data.frame(transp)

# Graph
# ggplot() initializes the plot object; data=dat1 specifies the data source
ggplot(data=dat1) +
  # geom_bar() adds a bar layer; mapping=aes() defines how data maps to visuals
  # fct_infreq(transp) reorders the categories of 'transp' by their frequency
  # geom_bar(mapping=aes(x=(transp))) +
  geom_bar(mapping=aes(x=fct_infreq(transp))) +
  # xlab() sets the label for the x-axis
  xlab("Transportations")

```

* ggplot(data=dat1):
  * This initializes the plot.
  * data=dat1 tells R to use your dataframe dat1 as the source of truth for the visualization.

* +:
  * In ggplot2, the plus sign is used to "layer" components on top of each other. You start with a base plot and then add layers (geoms, scales, labels).

* geom_bar():
  * This specifies the geometric object to use. geom_bar specifically creates bars where the height is proportional to the number of cases in each group (frequency).
* mapping=aes(x=...):
  * aes (Aesthetic mapping) defines how variables in your data are mapped to visual properties of the plot.
  * Here, we map the x-axis to your transportation data.
* fct_infreq(transp):
  * This is a function from the forcats package.
  * By default, ggplot orders categorical data alphabetically. fct_infreq reorders the categories of transp based on their frequency (count), so the most frequent transportation method appears first on the left.
* xlab("Transportations"):
  * This simply sets a custom user-friendly label for the X-axis.


  # 2-9

```{r}
library(ggplot2)

## factor : 순서형 범주형 변수로 인식, levels로 순서 지정
obesity <- factor(c("underweight", "normal", "overweight", "obese"),
                  levels = c("underweight", "normal", "overweight", "obese"))
count <- c(6, 69, 27, 13) # 빈도수
perc <- count/sum(count) * 100 # 백분율 계산
dat2 <- data.frame(obesity, count, perc)

# Graph
## stat="identity" : y축 값을 그대로 사용
## geom_bar()의 기본값은 stat="count"
## geom_col()은 stat="identity"가 기본값
ggplot(data=dat2) +
    geom_bar(mapping=aes(x=obesity, y=perc), stat="identity") +
    xlab("Obesity") +
    ylab("Percentage (%)")

```


# 2-10

```{r}
# Install forcats if not already installed
# install.packages("forcats")

# Load libraries
library(ggplot2)
library(forcats)



# Data
transp <- c("bycicle", "bus", "bus", "walking", "bus", "bycicle", "bycicle",
            "bus", "bus", "bus" , "bycicle", "bus", "bycicle", "bycicle", 
            "walking", "bus", "bus", "bicycle", "bicycle", "walking", "walking",
            "bicycle", "bus", "bus", "bus", "bus", "bicycle", "bus", "bus",
            "bicycle", "bicycle", "bicycle")

table(transp)
dat3 <- data.frame(transportation=c("bus", "bicycle", "walking"), count=c(15, 13, 4))

# Graph

ggplot(data=dat3) +
  geom_bar(mapping=aes(x="", y=count, fill=transportation), stat="identity") +
  coord_polar("y", start=0) +
  xlab("")

``` 

## fill: 색상을 지정하는 옵션, 
 ## y: y축의 값을 지정하는 옵션, 
 ## stat: 통계량을 지정하는 옵션, 
 ## coord_polar: 극좌표로 변환하는 옵션, 
 ## xlab: x축의 이름을 지정하는 옵션, 



 # 2-13
## breaks=n : 구간의 개수를 n개로 지정

```{r}
set.seed(2021)
rn <- c(rnorm(100, 5, 2), rnorm(100, 10, 2))

hist(rn)
hist(rn, breaks=20, main="", xlab="value")
hist(rn, breaks=5, main="", xlab="value")
```

# 2-14

```{r}
age <- c(57, 61, 47, 57, 48, 58, 57, 61, 64, 58, 68, 51)

m.age <- mean(age)
par(xpd=TRUE)
stripchart(age, axes=F, pch=19, xlim=c(45, 70), method="stack", offset=5, cex=1.5)
axis(1, at=seq(45, 70, 5))
points(m.age -5, pch=17, cex=2, col="blue")
```

# 2-15

```{r}

age <- c(57, 61, 47, 57, 48, 58, 57, 61, 54, 50, 68, 51)
boxplot(age, ylab="Age")

```

# 2-17

```{r}
member <- c(92, 107, 180, 90, 78, 91, 102, 88, 106, 125, 95, 102, 162)
boxplot(member, ylab="Number of board members")

```
